---
title: "Package Tutorial"
author: "Gaelyn Gros"
date: "`r Sys.Date()`"
output: html_document
---

# An Introduction to grosproj R package


*This package will be used to remove na's and to create a sampling location map, scatter plot, and linear model of a water quality dataset.*

My R package is applicable to a water quality dataset with a download link provided below. It includes **cleaning and filtering data, a linear model, mapping of sampling coordinates, and scatter plot of coordinate data.**

## Installation Instructions

**Step 1:** is to download the water quality data needed to use this package:
```{r eval=FALSE, include=TRUE}
download.file(url = "https://raw.githubusercontent.com/gaelyngros/Gros_pkg/master/data/ac_field_data.csv", destfile = filepath) 
```              

**Step 2:** is to download the packages needed for the package. :) 
```{r eval=FALSE, include=TRUE}
install.packages("tidyverse")
install.packages("leaflet")
install.packages("sf")
install.packages("mapview")
install.packages("ggplot2")
# These packages are required for full use of the grosproj package but are not required for every function.
```

Make sure to join the appropriate libraries after installing them:

```{r eval=FALSE, include=TRUE}
library(tidyverse)
library(leaflet)
library(sf)
library(mapview)
library(ggplot2)
```

## Using the grosproj

**Step 1:** The following codes are the functions included in my package, with first a data clean function where we create a new CSV file:

```{r eval=FALSE, include=TRUE}
clean_data <- function(filepath) {
  data_raw <- read_csv(filepath)
  data_clean <- data_raw %>%
    drop_na()
  write.csv(file = "ac_clean.csv", data_clean)
  return(is.na(data_clean))
}
```

Now that we have written a new csv file with no na's, let's assign that file to an object for the following functions:

```{r eval=FALSE, include=TRUE}
ac_clean <- read_csv("../data/ac_clean.csv")
```

**Step 2:** Now that we have assigned an object with our new clean dataframe, we can run the following functions using the object for the clean dataset:

Creating a scatterplot:
```{r eval=FALSE, include=TRUE}
scatp <- function(ac_clean) {
  scatp_raw <- ac_clean
  scatp_data <- scatp_raw
grouped_rivers_plot <- ggplot(scatp_data, aes(x = longitude, y = latitude, color = river)) + geom_point()
return(grouped_rivers_plot)
}
```

Running a linear model:
```{r eval=FALSE, include=TRUE}
lin_model <- function(ac_clean) {
  lin_data_raw <- ac_clean
  lin_data <- lin_data_raw 
  model_fit <- lm(latitude ~ longitude + river + longitude:river, data = lin_data)
  return(summary(model_fit))
  }
```

Filtering the data based on the river column:
```{r eval=FALSE, include=TRUE}
ouachita_filtered <- function(ac_clean) {
  ouachita_raw <- ac_clean
  ouachita_river <- ac_clean %>%  
    filter(month == 8) 
  return(ouachita_river)
}
```

```{r eval=FALSE, include=TRUE}
red_filtered <- function(ac_clean) {
  red_raw <- ac_clean
  red_river <- ac_clean %>%  
    filter(month == 6) 
  return(red_river)
}
```

```{r eval=FALSE, include=TRUE}
sabine_filtered <- function(ac_clean) {
  sabine_raw <- ac_clean
  sabine_river <- ac_clean %>%  
    filter(month == 6 & day <= 23) 
  return(sabine_river)
}
```

Creating a map of the sampling coordinates:
```{r eval=FALSE, include=TRUE}
leafmap <- function(ac_clean) {
leafmap_raw <- ac_clean
leafmap_data <- leafmap_raw
samples_leafmap <- leaflet(ac_clean) %>% 
addTiles() %>% 
  addCircleMarkers(~longitude, ~latitude, radius = runif(100, 4, 10), color = c('navy'))
return(samples_leafmap)
}
```

*More functions will be included in this package but they are not complete, to avoid interference with the operation of this package, the functions have been included elsewhere on my website for further work.*


**BONUS:** If you have any questions, you will not find the answer at kylepiller.com, however you may be interested in clicking the link anyway. [kylepiller.com/](kylepiller.com)


Random note for me to reference later:
![Caption](path/to/image)
